CFF GCT Study

### 2025-03-14 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
adult BMI values for GCT

---
title: "CFF GCT Study"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-height: 9
    fig-width: 12
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/Documents/GitHub/styles/american-medical-association.csl
editor: source
---

@@

@@

```{r results='asis'}
#| label: table1a
#| tbl-cap: Participant characteristics by OGTT status
#| message: false
# Basic table formula
f <- ~ HbA1c + kwt(Age, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Weight (kg)`, "N", "Nmiss2", "medianq1q3", "range") + `Height (cm)` +
  kwt(BMI, "N", "Nmiss2", "medianq1q3", "range") + Gender + fe(Race) +
  fe(Ethnicity) + fe(`Pancreatic insufficient`) +
  fe(`Type 2 diabetes in the family - Father`) +
  fe(`Type 2 diabetes in the family - Mother`) +
  fe(`Brothers (number with diabetes)`) + fe(`Sisters (number with diabetes)`) +
  kwt(
    `Number of other relatives with diabetes (aunts, uncles, cousins, grandparents)`,
    "N", "Nmiss2", "medianq1q3", "range"
  ) +
  `Highest FEV1pp` + `Second Highest FEV1pp` + `Average of Highest FEV1pp` +
  kwt(`GCT 0 min plasma`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 0 min capillary`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 60 min plasma`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 60 min capillary`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 0 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 60 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 120 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Height %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Weight %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`BMI %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Days From OGTT to GCT`, "N", "Nmiss2", "medianq1q3", "range") +
  fe(Diagnosis) + fe(Dysglycemia) + fe(Diabetes) + fe(CFRD)
t1a <- tableby(update(f, `Got OGTT and GCT?` ~ . - `Got OGTT and GCT?`),
  data = df, control = mycontrols
)
summary(t1a, pfootnote = T, digits = 2)
# Limit to 189 after this
df <- df %>%
  filter(`Got OGTT and GCT?` == "Have GCT 1 Hour Plasma or OGTT 2 Hour") %>%
  select(-`Got OGTT and GCT?`)
```

>>>>

---
title: "CFF GCT Study"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    fig-height: 9
    fig-width: 12
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /home/timvigers/Documents/Miscellaneous/zotero.bib
csl: /home/timvigers/Documents/GitHub/styles/american-medical-association.csl
editor: source
---

@@

df$`BMI Value (Adults Only)` <- df$BMI
df$`BMI Value (Adults Only)`[df$Age < 20] <- NA

@@

```{r results='asis'}
#| label: table1a
#| tbl-cap: Participant characteristics by OGTT status
#| message: false
# Basic table formula
f <- ~ HbA1c + kwt(Age, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Weight (kg)`, "N", "Nmiss2", "medianq1q3", "range") + `Height (cm)` +
  kwt(BMI, "N", "Nmiss2", "medianq1q3", "range") + Gender + fe(Race) +
  fe(Ethnicity) + fe(`Pancreatic insufficient`) +
  fe(`Type 2 diabetes in the family - Father`) +
  fe(`Type 2 diabetes in the family - Mother`) +
  fe(`Brothers (number with diabetes)`) + fe(`Sisters (number with diabetes)`) +
  kwt(
    `Number of other relatives with diabetes (aunts, uncles, cousins, grandparents)`,
    "N", "Nmiss2", "medianq1q3", "range"
  ) +
  `Highest FEV1pp` + `Second Highest FEV1pp` + `Average of Highest FEV1pp` +
  kwt(`GCT 0 min plasma`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 0 min capillary`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 60 min plasma`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`GCT 60 min capillary`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 0 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 60 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`OGTT 120 min`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Height %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Weight %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`BMI %ile`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`BMI Value (Adults Only)`, "N", "Nmiss2", "medianq1q3", "range") +
  kwt(`Days From OGTT to GCT`, "N", "Nmiss2", "medianq1q3", "range") +
  fe(Diagnosis) + fe(Dysglycemia) + fe(Diabetes) + fe(CFRD)
t1a <- tableby(update(f, `Got OGTT and GCT?` ~ . - `Got OGTT and GCT?`),
  data = df, control = mycontrols
)
summary(t1a, pfootnote = T, digits = 2)
# Limit to 189 after this
df <- df %>%
  filter(`Got OGTT and GCT?` == "Have GCT 1 Hour Plasma or OGTT 2 Hour") %>%
  select(-`Got OGTT and GCT?`)
```
